---
title: "ADD IN MEANINGFUL TITLE HERE"
author: "A2 GROUP NUMBER: ADD YOUR NAMES HERE"
subtitle: "STA304 - Fall 2025 - Assignment 1"
format: pdf
editor: visual
---

```{r, include = FALSE}

# Here you can load in and clean the data (you may need to do the cleaning in a separate R script - this is up to you). 
library(tidyverse)


# You may need additional chunks, in case you want to include some of the cleaning output.

```

# 1 Introduction

In this section you will briefly describe your report. Explain the importance of the survey you are going to present, as well as the subsequent analysis and prepare the reader for what they will read in the subsequent sections. Explain the goal/topic of the survey/study and the variables you selected of interest here. It might be helpful to explain what STEMBuddies is and provide some information/literature review about education resource developement. You will likely need to include in-line citations/references (you can APA style/formatting if desired \[1\]).

# 2 Survey Showcasing

## 2.1 Survey Description

Provide a link to your survey. Here is an example of how to put a url into your document: <https://www.surveymonkey.co.uk/r/99CGC3B>. Remember the survey needs to include:

(i) Introduction section
(ii) at least 2 demographic survey questions
(iii) At least 2 needs assessments survey questions
(iv) Conclusion/closing message.

Briefly describe your survey theme/focus. Comment on questions that were included and justify any categorizations.

## 2.2 Testing My Survey

Briefly describe how you tested your survey.

## 2.3 Showcasing Relevant Question(s)

Choose at least 1 question in your survey to showcase in this submission (as well as any other questions that are relevant to analyses in subsequent sections). You can format this however you'd like, but we prefer it to be organized and be easily readable given the question type. It might be a good idea to italicize the question(s) you are showcasing. Copy and paste the question(s) (and make sure they are formatted nicely) into this section of the document. Explain why you chose this question(s) and the benefits and drawbacks of the design/wording of the question. For each drawback you list, justify why you couldn’t avoid/address it in the design of your survey.

# 3 Procedure

## 3.1 Proposed Sampling Procedure

Briefly introduce the proposal and how you would recommend STEMBuddies implement the sampling process of collecting survey feedback (ie. provide a procedural outline of how you propose STEMBuddies should collect the data from the population - try to be realistic).

Here you should identify a target population, a reasonable sampling frame (if you are suggesting using one), and the (proposed) sample units. Try to be reasonable. Identify the strengths of your proposed sampling procedure and highlight any potential errors/biases.

## 3.2 Simulation

Type here a paragraph introducing the data that you will simulate (i.e., for the question/variables introduced in Section 3 - Survey Showcasing), its context and the data simulation process. Be sure that your description is reproducible and that the simulated values match the inputs expected from your survey.

```{r, include = FALSE}

# Here you can simulate and clean the data. 

# You may need additional chunks, in case you want to include some of the cleaning output. 

# I have included some example code below, but it should be changed, as it is likely not relevant and doesn't really appropriately simulate heights.

set.seed(1234)
height <- runif(n=5, min=0, max=4)
friendly <- sample(x=c("yeah", "No"), size=5, replace=T)

sim_data <- tibble(height, friendly)

```

# 4 Data

Briefly introduce the data and key variables of interest. If you do any general data cleaning or data processing you should describe it (in a reproducible manner) here. It might be helpful to clearly define the variables of interest (i.e., the ones you will present in the subsequent sections) here, along with any data cleaning you did to these variables.

```{r, include = FALSE}

# Here you can clean your data (if needed). 

# Below is an example of me changing the "yeah"s to "Yes"s

sim_data_clean <- sim_data %>% 
  mutate(friendly_clean  = case_when(friendly=="yeah" ~ "Yes",
                                     friendly=="No"~"No")) %>% 
  select(-friendly)

```

```{r, echo = FALSE}

# Use this to create some plots. 

sim_data_clean %>% ggplot(aes(x=friendly_clean))+
  geom_bar(fill="orange", col="brown") +
  theme_minimal() + 
  labs(x = "Friendly",
       y = "Frequency",
       title = "Figure 1: A bar plot displaying whether the student thinks that \n they are a friendly person or not for all students \n in highschools measured in Ontario.") 

```

# 5 Methods

Include some text introducing the methodology. Here you should describe the confidence interval and all of the components.

$$ include.your.mathematical.model.here.if.you.have.some.math.to.show $$

Here is an example of a non-sensical CI that the prof made up, but has math coding components that you can change accordingly:

$$\bar{X} \pm \chi_{\alpha/2} \sqrt{\frac{1+1}{n}}$$

\<Here you should describe the CI. Here is an example with a citation:\>

I will invoke a non-parametric bootstrap \[2\] to derive the 95% confidence interval (CI) for the mean age of students in STA304.

# 6 Results

```{r, include = FALSE}

# Here you can derive the CIs of interest based off the simulated data in a previous chunk.

```

Remind the reader of what your variable is. Here you could present your results. You may want to put them into a well formatted table. Be sure that there is some text describing the results.

In Table 1 I present both confidence intervals of... Compare the confidence intervals of the same outcome of the two surveys. Be sure to highlight any key takeaways of the results and how this relays to the populations at hand and how it relates back to the motivations you laid out in your Introduction section.

|   | Proportion of Outcome Variable | 95% Confidence Interval of Outcome Variable |
|----|----|----|
| My Survey Q | 0.34 | (lower bound, upper bound) |
| Another Survey Q | 0.25 | (lower bound, upper bound) |

: The proportions and 95% confidence intervals of outcome variable of interest calculated for both my survey question and another survey question.

# 7 Generative AI Statement

Here is where you can explain your usage of Generative AI tool(s). Be sure to reference it.

Alternatively, if you did not use Generative AI, please include a brief statement outlining your workflow for completing this assignment.

# 8 Bibliography

1.  Schwartz, B. M., Landrum, R. E., & Gurung, R. A. (2020). *An easyguide to APA style*. Sage Publications.

2.  Dekking, F. M., et al. (2005) *A Modern Introduction to Probability and Statistics: Understanding why and how.* Springer Science & Business Media.

3.  Allaire, J.J., et. el. *References: Introduction to R Markdown*. RStudio. <https://rmarkdown.rstudio.com/docs/>. (Last Accessed: April 4, 1991)

# 9 Appendix

## 9.1 Survey questions

Below is a well formatted copy of all of my survey questions (along with the opening and closing messages/statements).

## 9.2 Simulated Survey Data

Below is a `glimpse()` or `head()` of my simulated data (this should be the data that looks like the inputs from your survey). This is the only place in the report where you can show your raw R code and output.

```{r, echo=TRUE}
head(sim_data)
```

## 9.3 Supplementary Materials

Any other supplementary items you wish to include (e.g., more plots, derivations, etc.) can be in this sub section.
