---
title: "STEMBuddies Handbook Survey"
author: "\\small A1-GROUP 40: ISLA CHEONG, VANESSA GABRIELA KWOK, MIA SUNG, CAROL XU"
subtitle: "STA304 - Fall 2025 - Assignment 1"
format: pdf
fontsize: 12pt
geometry: margin=2.5cm
editor: visual
---

```{r, include = FALSE}

# Here you can load in and clean the data (you may need to do the cleaning in a separate R script - this is up to you). 
library(tidyverse)


# You may need additional chunks, in case you want to include some of the cleaning output.

```

# 1 Introduction

Planning for high school and preparing for college applications can be extremely complex for students who lack experience and support, particularly for those from low-income and underrepresented groups. However, providing these students with adequate information and guidance can encourage them to apply to and gain admission to colleges with richer educational resources and higher academic standards \[4\]. The High School Handbook developed by STEMBuddies has the potential to provide such guidance. To more effectively support students in their academic planning, financial needs, and personal development, it is necessary to collect feedback from current students on the handbook to assess their needs and preferences.

This report outlines the design and analysis of a survey created to assess the needs of high school students and their preferences. By using best practices in survey design \[2\], the survey provides actionable insights for STEMBuddies to improve the handbook accessibility, inclusivity, and their overall impact.

# 2 Survey Showcasing

## 2.1 Survey Description

Our survey, hosted on <https://forms.gle/sWqTQ1HCXPrjkk6BA>, is designed to gather insights from high school students regarding their academic and personal needs, as well as their preferences for mentorship programs. The survey consists of the following sections:

1.  **Introduction**: A brief description of STEMBuddies and purpose of the survey.
2.  **Core Questions**: Demographic questions, needs-assessment questions, and program feedback prompts.
3.  **Closing Message**: Thanks participants and provides contact information.

## 2.2 Testing My Survey

Each question was designed to minimize ambiguity and cognitive load. For example, we avoided double-barreled items and ensured that the survey was focused and concise \[2\]. We piloted the survey with three peers in different grade levels and incorporated feedback to refine clarity and ease of responsiveness. Based on the feedback, we improved on word selection and question setting.

## 2.3 Showcasing Relevant Question(s)

A key survey question is showcased below:

*Which of the following resources would be most valuable to you in the STEMBuddies program? (Select up to three options)*

-   Academic Tutoring
-   College Application Guidance
-   Career Counseling
-   Mental Health Support
-   Time Management Skills
-   Financial Literacy
-   Other: \_\_\_\_\_\_\_\_\_\_\_

We choose this question because it provides insight into what our target population may be seeking in the handbook and helps us better understand their needs.

The benefit of this type of question is that the multiple-choice format, combined with an ‘Other’ option, provides both structure and flexibility. It allows participants to choose from common resources while also giving them space to share needs that may not be listed. However, a drawback is that some nuanced or specific needs might still be overlooked, either because participants do not think to write them in or because they feel limited by the predefined options. This drawback is unavoidable while we want to keep the answering process easy and short, but the following question ("What challenges or barriers are preventing you from pursuing STEM?") may help us understand the students' needs better.

# 3 Procedure

## 3.1 Proposed Sampling Procedure

To collect survey feedback, we propose a stratified random sampling procedure targeting high school students across Canada, with the individual student serving as the sampling unit \[5\]. The survey will be distributed to students via partnerships with high schools, provincial boards, mailing lists, STEM clubs, outreach initiatives, and educational organizations that cater to diverse student populations in order to acquire the sampling frame. The survey can be conducted in-class with teacher oversight to boost response rates or online using unique survey links shared through schools and partner organizations.

This method guarantees representation across various strata such as geographic area, school category (public or private), and socioeconomic level. The sampling frame is limited but feasible. Errors may arise from coverage bias (because some schools or students may not be included in the frame), non-response bias (students who are absent or less engaged choose not to participate), and limited internet access in rural or low-income areas \[1\]. Potential biases include self-selection bias, since the students who volunteer to answer the questionnaire might be more interested or motivated in high school planning, which means they possibly have more information on covered topics and underestimate/overestimate the helpfulness of specific topics.

## 3.2 Simulation

We simulate survey responses for 100 students to mirror the showcased resource-preference question. Each simulated respondent selects up to three resources from the options provided in the survey. This process ensures that the simulated dataset reflects the structure and response style of the actual survey, while still being reproducible through the use of a fixed random seed. By generating these responses, we create a realistic dataset that can be analyzed to demonstrate the kinds of insights STEMBuddies could obtain if the survey were administered in practice.

```{r, include = FALSE}

# Here you can simulate and clean the data. 

# You may need additional chunks, in case you want to include some of the cleaning output. 

# I have included some example code below, but it should be changed, as it is likely not relevant and doesn't really appropriately simulate heights.

# set.seed(1234)
# height <- runif(n=5, min=0, max=4)
# friendly <- sample(x=c("yeah", "No"), size=5, replace=T)
# 
# sim_data <- tibble(height, friendly)

set.seed(1234)
n <- 100
resources <- c("Academic Tutoring", "College Application Guidance", "Career Counseling",
               "Mental Health Support", "Time Management Skills", "Financial Literacy", "Other")

# sim_data <- tibble(
#  id = 1:n,
#  resource1 = sample(resources, n, replace = FALSE),
#  resource2 = sample(resources, n - 1, replace = FALSE),
#  resource3 = sample(resources, n, replace = FALSE)
#)

# Ensure unique selections for each student
sim_data <- tibble(id = 1:n) %>%
  rowwise() %>%  # Process each row individually
  mutate(
    resource1 = sample(resources, 1),  # First resource
    remaining_resources = list(resources[resources != resource1]),  # Remove the first choice
    resource2 = sample(remaining_resources, 1),  # Second resource (unique)
    resource3 = sample(remaining_resources[remaining_resources != resource2], 1)  # Third resource (unique)
  ) %>%
  select(id, resource1, resource2, resource3)  # Keep only the needed columns

```

# 4 Data

## 4.1 Data Cleaning and Processing

The dataset consists of simulated survey responses from 100 high school students. Each student was asked to select up to three resources they would find most valuable from a list that included options such as Academic Tutoring, College Application Guidance, and Financial Literacy.

To prepare the data for analysis, we reshaped the responses into a long format, where each selected resource for a student appeared as a separate entry. This helps us to summarize selections across all students. Next, we converted the data into a binary format, creating separate indicator variables for each resource. In this structure, a value of 1 indicates that a student selected the resource, and 0 indicates they did not.

The main variables are the binary indicators for each resource, showing whether a student selected it. This cleaned format allows for consistent, reproducible analysis of overall resource preferences.

```{r, include = FALSE}

# # Here you can clean your data (if needed). 
# 
# # Below is an example of me changing the "yeah"s to "Yes"s
# 
# sim_data_clean <- sim_data %>% 
#   mutate(friendly_clean  = case_when(friendly=="yeah" ~ "Yes",
#                                      friendly=="No"~"No")) %>% 
#   select(-friendly)

# Reshape to long format
sim_data_clean <- sim_data %>%
  pivot_longer(cols = starts_with("resource"), names_to = "resource_num", values_to = "resource") %>%
  select(-resource_num)

# Create binary-coded dataset
sim_data_binary <- sim_data_clean %>%
  mutate(value = 1) %>%
  complete(id, resource, fill = list(value = 0)) %>%  # Fill missing with 0
  pivot_wider(
    id_cols = id,
    names_from = resource,
    values_from = value 
  )
```

## 4.2 Variables of Interest

The main analysis focuses on the survey question: “Which of the following resources would be most valuable to you in the STEMBuddies program? (Select up to three options).” Each resource is represented as a binary-coded variable (0 = not selected, 1 = selected). The key variables analyzed are: Academic Tutoring, College Application Guidance, Career Counseling, Mental Health Support, Time Management Skills, Financial Literacy, and Other. These variables form the core of the main analysis, allowing us to calculate the frequency and proportion of students selecting each resource, visualize student preferences, and compute confidence intervals to quantify the uncertainty around these proportions.

## 4.3 Figures

```{r, fig.width=7, fig.height=5, echo = FALSE}

# # Use this to create some plots. 
# 
# sim_data_clean %>% ggplot(aes(x=friendly_clean))+
#   geom_bar(fill="orange", col="brown") +
#   theme_minimal() + 
#   labs(x = "Friendly",
#        y = "Frequency",
#        title = "Figure 1: A bar plot displaying whether the student thinks that \n they are a friendly person or not for all students \n in highschools measured in Ontario.") 

sim_data_clean %>%
  ggplot(aes(x = resource)) +
  geom_bar(fill = "blue", col = "black") +
  theme_minimal() +
  labs(x = "Resource",
       y = "Frequency",
       title = "Figure 1: Frequency of Resource Preferences Among High School Students") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

Figure 1 shows the number of students who selected each resource from the survey. The x-axis lists all possible resources, while the y-axis represents the number of students selecting each option. Among the listed resources, Financial Literacy had the highest frequency of selection, while Time Management Skills had the lowest. This figure clearly highlights which resources are most frequently requested, providing STEMBuddies with a visual summary of student preferences. For example, taller bars indicate higher demand for a particular resource, helping to prioritize support areas in the handbook.

## 4.4 Data Summary for Confidence Interval Analysis

The cleaned survey data allows us to calculate the proportion of students who selected each resource. With the variables coded as 0 or 1, these proportions give a clear view of student demand. This summary also provides a useful information for constructing confidence intervals, which highlight the uncertainty in our estimates and how they may generalize to the broader student population.

# 5 Methods

To estimate the proportion of students who prefer a specific resource, we will use the following formula for a 95% confidence interval for a population proportion: $$CI = \hat{p} \pm z^*  \sqrt{\frac{\hat{p}(1-\hat{p})}{n}}$$where $\hat{p}$ is the sample proportion, $z^∗$ is the critical value from the standard normal distribution (z-score) corresponding to the desired confidence level (1.96 for 95% confidence), and n is the sample size \[3\]. The value under the square root represents the standard error, reflecting the variability expected from repeated student sampling, and multiplying it by $z^∗$ gives the margin of error. This method assumes a large enough sample size to support the normal approximation and that student responses are independent of each other. With these conditions, a 95% confidence interval indicates that if the survey were repeated many times, about 95% of the constructed intervals would capture the true population proportion.

# 6 Results

```{r, include = FALSE}

# Here you can derive the CIs of interest based off the simulated data in a previous chunk.

# Below is some example code that calculates the CI for the proportion of students that think they are friendly. You will need to change this to be relevant to your survey question/variable of interest.

n <- nrow(sim_data_clean)
p_hat <- sim_data_clean %>% filter(resource == "Academic Tutoring") %>% nrow() / n
z_star <- 1.96
margin_of_error <- z_star * sqrt((p_hat * (1 - p_hat)) / n)
ci_lower <- p_hat - margin_of_error
ci_upper <- p_hat + margin_of_error

# Here is an example of printing out the results. You will need to change this to be relevant to your survey question/variable of interest.

cat("Proportion of students preferring Academic Tutoring:", round(p_hat, 2), "\n")
cat("95% Confidence Interval: (", round(ci_lower, 2), ",", round(ci_upper, 2), ")\n")

```

| Resource          | Proportion of Students | 95% Confidence Interval |
|-------------------|------------------------|-------------------------|
| Academic Tutoring | 0.12                   | (0.08, 0.16)            |

: The proportion and 95% confidence interval of students preferring "Academic Tutoring".

Interpretation: For example, 12% of students selected "Academic Tutoring" as a valuable resource, and the confidence interval suggests that the true proportion is likely between 8% and 16%.

# 7 Generative AI Statement

Generative AI (ChatGPT) was used to help structure this report, generate simulation code, and ensure clarity of statistical explanations. AI was also used selectively to enhance grammar, improve clarity of expression, and suggest alternative phrasing for technical material. All simulated data generation, results, and interpretation were conducted independently by the authors. Although AI can enhance clarity and efficiency, it has notable limitations: its outputs may include factual or methodological errors, and it lacks the critical reasoning required for proper statistical validation. To address this concern, all AI-generated outputs were thoroughly reviewed, verified against course materials and reliable sources, and rewritten or adapted to reflect the authors’ own understanding. 

# 8 Bibliography

1.  Stantcheva, S. (2022) *How To Run Surveys: A guide to create your own identifying variation and revealing the invisible.* <https://scholar.harvard.edu/files/stantcheva/files/How_to_run_surveys_Stantcheva.pdf>

2. *Creating Effective Surveys: Best Practices in Survey Design.* Evidence Use in Education. (2021). Regional Educational Laboratory West. <https://eric.ed.gov/?id=ED619797>.

3.  Dekking, F.M., et al. (2005) *A Modern Introduction to Probability and Statistics: Understanding why and how.* Springer Science & Business Media.

4.  Hoxby, C., & Turner, S. (2014). Expanding College Opportunities for High-Achieving, Low Income Students. <https://eml.berkeley.edu/~saez/course131/Hoxby-Turner13.pdf>.

5.  Wu, C.B. & Thompson, M.E. (2020) *Sampling Theory and Practice.* Springer Nature Switzerland AG.

# 9 Appendix

## 9.1 Survey questions

Below is a well formatted copy of all of our survey questions (along with the opening and closing messages/statements).

**Introduction**

This is the STEMBuddies Handbook Survey!

Mentorship is a resource that aids students in finishing high school and getting ready for higher education, especially in science, technology, engineering, and mathematics (STEM) areas. STEMBuddies is a group that connects high school students with mentors, organizes workshops, offers programs centered on post-secondary education, and supplies free resources to decrease obstacles for underrepresented communities.

We appreciate your participation. STEMBuddies Handbook is a resource designed to support high school students in their academic and personal journeys in STEM and your feedback will provide valuable information to improve it.

This questionnaire will require approximately 5 minutes to finish. Your responses are confidential, anonymous, and will only be used to improve the STEMBuddies Handbook.

**Section 1: Demographics**

1\. You are in Grade

-   9

-   10

-   11

-   12

-   Other: \_\_\_\_\_\_\_\_\_\_

2\.  What gender do you identify with?

-   Female

-   Male

-   Prefer not to say

-   Other: \_\_\_\_\_\_\_\_\_\_

3\.  What racial or ethnic group describes you?

-   Indigenous (First Nations, Métis, Inuit)
-   Black
-   East Asian
-   Latino
-   Middle Eastern
-   South Asian
-   South East Asian
-   White
-   Other: \_\_\_\_\_\_\_\_\_\_

4\. Select your school type

-   Public

-   Private

-   Other: \_\_\_\_\_\_\_\_\_\_

5\. Which of the following best describes your current academic program?

-   Mainstream (OSSD only)
-   AP
-   IB
-   Other: \_\_\_\_\_\_\_\_\_\_

6\. Which is your province or territory of residence?

-   Ontario
-   Quebec
-   Nova Scotia
-   New Brunswick
-   Manitoba
-   British Columbia
-   Prince Edward Island
-   Saskatchewan
-   Alberta
-   Newfoundland and Labrador
-   Northwest Territories
-   Yukon
-   Nunavut

**Section 2: Needs and Feedback**

1\.  On a scale from 1 (not helpful) to 5 (extremely helpful), how helpful do you think a handbook resource would be for supporting you in your STEM journey?

-   1 (Not Helpful)

-   2

-   3

-   4

-   5 (Extremely Helpful)

2\. Which areas of the handbook do you think need the most improvement? (Select all that apply)

-   Course planning and prerequisites

-   AP/IB pathway guidance

-   Study strategies

-   Extracurriculars and competitions

-   University admissions (OUAC, supplementary applications)

-   Scholarships and financial aid

-   U.S. application process

-   Other: \_\_\_\_\_\_\_\_\_\_

3\. Which of the following resources would be most valuable to you as part of the STEMBuddies program? (Select up to three options)

-   Academic Tutoring
-   College Application
-   Guidance Career Counseling
-   Financial Literacy
-   Mental Health Support
-   Time Management Skills
-   University/Program Information
-   Other: \_\_\_\_\_\_\_\_\_\_

4\. What challenges or barriers are preventing you from pursuing STEM? (Select all that apply)

-   Lack of information about post-secondary programs
-   Limited access to mentors/role models
-   Financial concerns
-   Difficulty in certain STEM subjects
-   Family or community expectations
-   Other: \_\_\_\_\_\_\_\_\_\_

**Section 3: Open Feedback**

1\.  What additional content or features would you like to see included in the STEMBuddies Handbook?

**Closing Message (Sent as a Confirmation Message)**

Thanks so much for giving us feedback!

The STEMBuddies Handbook will incorporate your feedback and ensure it satisfies the needs of students like you. Thanks to your help, we can make STEM pathways accessible to all Canadian high school students.

If you want to learn more about STEMBuddies and all the STEMBuddies resources, please visit: https://stembuddies.ca.

## 9.2 Simulated Survey Data

Below is a `glimpse()` or `head()` of my simulated data (this should be the data that looks like the inputs from your survey). This is the only place in the report where you can show your raw R code and output.

```{r, echo=TRUE}
head(sim_data)
```

## 9.3 Supplementary Materials

Any other supplementary items you wish to include (e.g., more plots, derivations, etc.) can be in this sub section.
