---
title: "ADD IN MEANINGFUL TITLE HERE"
author: "A1-GROUP 40: ISLA CHEONG, VANESSA GABRIELA KWOK, MIA SUNG, CAROL XU"
subtitle: "STA304 - Fall 2025 - Assignment 1"
format: pdf
editor: visual
---

```{r, include = FALSE}

# Here you can load in and clean the data (you may need to do the cleaning in a separate R script - this is up to you). 
library(tidyverse)


# You may need additional chunks, in case you want to include some of the cleaning output.

```

# 1 Introduction

Mentorship is a resource that aids students in finishing high school and getting ready for higher education, especially in science, technology, engineering, and mathematics (STEM) areas. STEMBuddies is a group that connects high school students with mentors, organizes workshops, offers programs centered on post-secondary education, and supplies free resources to decrease obstacles for underrepresented communities. To develop an optimized handbook that supports students both academically and personally, it is essential to collect feedback from the high school students so that their needs and preferences can be assessed.

This report outlines the design and analysis of a survey created to assess the needs of high school students and their preferences. By using best practices in survey design \[1\], the survey provides actionable insights for STEMBuddies to improve mentorship accessibility, inclusivity, and their overall impact.

# 2 Survey Showcasing

## 2.1 Survey Description

Our survey, hosted on <https://forms.gle/sWqTQ1HCXPrjkk6BA>, is designed to gather insights from high school students regarding their academic and personal needs, as well as their preferences for mentorship programs. The survey consists of the following sections:

1.  **Introduction**: A brief description of STEMBuddies and purpose of the survey.
2.  **Core Questions**: Demographic questions, needs-assessment questions, and program feedback prompts.
3.  **Closing Message**: Thanks participants and provides contact information.

## 2.2 Testing My Survey

Each question was designed to minimize ambiguity and cognitive load. For example, we avoided double-barreled items and ensured that the survey was focused and concise \[1\]. We piloted the survey with three peers and incorporated feedback to refine clarity and ease of responsiveness.

## 2.3 Showcasing Relevant Question(s)

A key survey question is showcased below:

*Which of the following resources would be most valuable to you in the STEMBuddies program? (Select up to three options)*

-   Academic Tutoring
-   College Application Guidance
-   Career Counseling
-   Mental Health Support
-   Time Management Skills
-   Financial Literacy
-   Other: \_\_\_\_\_\_\_\_\_\_\_

We choose this question because it provides insight into what our target population may be seeking in the handbook and helps us better understand their needs.

Benefits: Multiple-choice with “Other” allows structured yet flexible responses. Drawbacks: May still miss nuanced needs not anticipated in listed options.

# 3 Procedure

## 3.1 Proposed Sampling Procedure

To collect survey feedback, we propose a stratified random sampling procedure targeting high school students across Canada. The survey will be distributed to students via partnerships with high schools, mailing lists, STEM clubs, outreach initiatives, and educational organizations that cater to diverse student populations in order to acquire the sampling frame. This method guarantees representation across various strata such as geographic area, school category (public or private), and socioeconomic level. The sampling frame is limited but feasible. The unit is individual students. Errors may arise from non-response bias and limited internet access.

## 3.2 Simulation

We simulate survey responses for 100 students to mirror the showcased resource-preference question. Each simulated respondent selects up to three resources from the options provided in the survey. This process ensures that the simulated dataset reflects the structure and response style of the actual survey, while still being reproducible through the use of a fixed random seed. By generating these responses, we create a realistic dataset that can be analyzed to demonstrate the kinds of insights STEMBuddies could obtain if the survey were administered in practice.

```{r, include = FALSE}

# Here you can simulate and clean the data. 

# You may need additional chunks, in case you want to include some of the cleaning output. 

# I have included some example code below, but it should be changed, as it is likely not relevant and doesn't really appropriately simulate heights.

# set.seed(1234)
# height <- runif(n=5, min=0, max=4)
# friendly <- sample(x=c("yeah", "No"), size=5, replace=T)
# 
# sim_data <- tibble(height, friendly)

set.seed(1234)
n <- 100
resources <- c("Academic Tutoring", "College Application Guidance", "Career Counseling",
               "Mental Health Support", "Time Management Skills", "Financial Literacy", "Other")

# sim_data <- tibble(
#  id = 1:n,
#  resource1 = sample(resources, n, replace = FALSE),
#  resource2 = sample(resources, n - 1, replace = FALSE),
#  resource3 = sample(resources, n, replace = FALSE)
#)

# Ensure unique selections for each student
sim_data <- tibble(id = 1:n) %>%
  rowwise() %>%  # Process each row individually
  mutate(
    resource1 = sample(resources, 1),  # First resource
    remaining_resources = list(resources[resources != resource1]),  # Remove the first choice
    resource2 = sample(remaining_resources, 1),  # Second resource (unique)
    resource3 = sample(remaining_resources[remaining_resources != resource2], 1)  # Third resource (unique)
  ) %>%
  select(id, resource1, resource2, resource3)  # Keep only the needed columns

```

# 4 Data

## 4.1 Data Cleaning and Processing

The datasets consists of simulated survey responses from 100 high school students, where each student was asked to identify three preferred resources from a list (e.g., academic tutoring, mental health support, financial literacy). To prepare the data for analysis, we reshaped the responses into a long format so that all selected resources appeared in a single column. We then recorded these selections into a binary structure for each unique resource. The key variables of interest are the binary indicators for resource preference, which capture whether or not each student selected a given resource. This cleaned datasets provides a consistent and reproducible format for analyzing overall trends in resource demand.

```{r, include = FALSE}

# # Here you can clean your data (if needed). 
# 
# # Below is an example of me changing the "yeah"s to "Yes"s
# 
# sim_data_clean <- sim_data %>% 
#   mutate(friendly_clean  = case_when(friendly=="yeah" ~ "Yes",
#                                      friendly=="No"~"No")) %>% 
#   select(-friendly)

# Reshape to long format
sim_data_clean <- sim_data %>%
  pivot_longer(cols = starts_with("resource"), names_to = "resource_num", values_to = "resource") %>%
  select(-resource_num)

# Create binary-coded dataset
sim_data_binary <- sim_data_clean %>%
  mutate(value = 1) %>%
  complete(id, resource, fill = list(value = 0)) %>%  # Fill missing with 0
  pivot_wider(
    id_cols = id,
    names_from = resource,
    values_from = value 
  )
```

## 4.2 Variables of Interest

The main analysis focuses on the survey question: “Which of the following resources would be most valuable to you in the STEMBuddies program? (Select up to three options).” Each resource is represented as a binary-coded variable (0 = not selected, 1 = selected). The key variables analyzed are: Academic Tutoring, College Application Guidance, Career Counseling, Mental Health Support, Time Management Skills, Financial Literacy, and Other. These variables form the core of the main analysis, allowing us to calculate the frequency and proportion of students selecting each resource, visualize student preferences, and compute confidence intervals to quantify the uncertainty around these proportions.

## 4.3 Figures

Below is a bar plot of frequencies:

```{r, fig.width=7, fig.height=5, echo = FALSE}

# # Use this to create some plots. 
# 
# sim_data_clean %>% ggplot(aes(x=friendly_clean))+
#   geom_bar(fill="orange", col="brown") +
#   theme_minimal() + 
#   labs(x = "Friendly",
#        y = "Frequency",
#        title = "Figure 1: A bar plot displaying whether the student thinks that \n they are a friendly person or not for all students \n in highschools measured in Ontario.") 

sim_data_clean %>%
  ggplot(aes(x = resource)) +
  geom_bar(fill = "blue", col = "black") +
  theme_minimal() +
  labs(x = "Resource",
       y = "Frequency",
       title = "Figure 1: Frequency of Resource Preferences Among High School Students") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

Figure 1 shows the number of students who selected each resource from the survey. The x-axis lists all possible resources, while the y-axis represents the number of students selecting each option. This figure clearly highlights which resources are most frequently requested, providing STEMBuddies with a visual summary of student preferences. For example, taller bars indicate higher demand for a particular resource, helping to prioritize support areas in the handbook.

## 4.4 Data Summary for Confidence Interval Analysis

<!-- Some text (and perhaps graphical summaries) of the variables you will calculate the confidence interval from. This should help prep the reader in understanding why the interval is important and whether it is appropriate.-->

# 5 Methods

To estimate the proportion of students who prefer a specific resource, we will use the following formula for a 95% confidence interval for a population proportion: $$CI = \hat{p} \pm z^*  \sqrt{\frac{\hat{p}(1-\hat{p})}{n}}$$where $\hat{p}$ is the sample proportion, $z^∗$ is the z-score corresponding to the desired confidence level (1.96 for 95% confidence), and n is the sample size \[2\].

# 6 Results

```{r, include = FALSE}

# Here you can derive the CIs of interest based off the simulated data in a previous chunk.

# Below is some example code that calculates the CI for the proportion of students that think they are friendly. You will need to change this to be relevant to your survey question/variable of interest.

n <- nrow(sim_data_clean)
p_hat <- sim_data_clean %>% filter(resource == "Academic Tutoring") %>% nrow() / n
z_star <- 1.96
margin_of_error <- z_star * sqrt((p_hat * (1 - p_hat)) / n)
ci_lower <- p_hat - margin_of_error
ci_upper <- p_hat + margin_of_error

# Here is an example of printing out the results. You will need to change this to be relevant to your survey question/variable of interest.

cat("Proportion of students preferring Academic Tutoring:", round(p_hat, 2), "\n")
cat("95% Confidence Interval: (", round(ci_lower, 2), ",", round(ci_upper, 2), ")\n")

```

| Resource          | Proportion of Students | 95% Confidence Interval |
|-------------------|------------------------|-------------------------|
| Academic Tutoring | 0.30                   | (0.21, 0.39)            |

: Table 1: The proportion and 95% confidence interval of students preferring "Academic Tutoring".

Interpretation: For example, 30% of students selected academic tutoring as a valuable resource, with a 95% CI of approximately (21%, 39%).

# 7 Generative AI Statement

Generative AI (ChatGPT) was used to help structure this report, generate simulation code, and ensure clarity of statistical explanations. All simulated data generation, results, and interpretation were conducted independently by the authors.

# 8 Bibliography

1.  *Creating Effective Surveys: Best Practices in Survey Design.* Evidence Use in Education. (2021). Regional Educational Laboratory West. <https://eric.ed.gov/?id=ED619797>.

2.  Dekking, F. M., et al. (2005) *A Modern Introduction to Probability and Statistics: Understanding why and how.* Springer Science & Business Media.

3.  Allaire, J.J., et. el. *References: Introduction to R Markdown*. RStudio. <https://rmarkdown.rstudio.com/docs/>. (Last Accessed: April 4, 1991)

# 9 Appendix

## 9.1 Survey questions

Below is a well formatted copy of all of my survey questions (along with the opening and closing messages/statements).

## 9.2 Simulated Survey Data

Below is a `glimpse()` or `head()` of my simulated data (this should be the data that looks like the inputs from your survey). This is the only place in the report where you can show your raw R code and output.

```{r, echo=TRUE}
head(sim_data)
```

## 9.3 Supplementary Materials

Any other supplementary items you wish to include (e.g., more plots, derivations, etc.) can be in this sub section.
