---
title: "ADD IN MEANINGFUL TITLE HERE"
author: "A1-GROUP 40: ISLA CHEONG, VANESSA GABRIELA KWOK, MIA SUNG, CAROL XU"
subtitle: "STA304 - Fall 2025 - Assignment 1"
format: pdf
editor: visual
---

```{r, include = FALSE}

# Here you can load in and clean the data (you may need to do the cleaning in a separate R script - this is up to you). 
library(tidyverse)


# You may need additional chunks, in case you want to include some of the cleaning output.

```

# 1 Introduction

<!-- In this section you will briefly describe your report. Explain the importance of the survey you are going to present, as well as the subsequent analysis and prepare the reader for what they will read in the subsequent sections. Explain the goal/topic of the survey/study and the variables you selected of interest here. It might be helpful to explain what STEMBuddies is and provide some information/literature review about education resource developement. You will likely need to include in-line citations/references (you can APA style/formatting if desired \[1\]). -->

Mentorship is a resource that aids students in finishing high school and getting ready for higher education, especially in science, technology, engineering, and mathematics (STEM) areas. STEMBuddies is a group that connects high school students with mentors, organizes workshops, offers programs centered on post-secondary education, and supplies free resources to decrease obstacles for underrepresented communities. To develop an optimized handbook that supports students both academically and personally, it is essential to collect feedback from the high school students so that their needs and preferences can be assessed.

This report outlines the design and analysis of a survey created to assess the needs of high school students and their preferences. By using best practices in survey design \[1\], the survey provides actionable insights for STEMBuddies to improve mentorship accessibility, inclusivity, and their overall impact.

# 2 Survey Showcasing

## 2.1 Survey Description

<!-- Provide a link to your survey. Here is an example of how to put a url into your document: <https://www.surveymonkey.co.uk/r/99CGC3B>. Remember the survey needs to include: -->

<!-- (i) Introduction section -->

<!-- (ii) at least 2 demographic survey questions -->

<!-- (iii) At least 2 needs assessments survey questions -->

<!-- (iv) Conclusion/closing message. -->

<!-- Briefly describe your survey theme/focus. Comment on questions that were included and justify any categorizations. -->

Our survey, hosted on <https://docs.google.com/forms/d/e/1FAIpQLSdYZMej-0D-irmDJD0RqHR06-R43lzvgS9Jn0mq6_WxutFUEw/viewform?usp=header>, is designed to gather insights from high school students regarding their academic and personal needs, as well as their preferences for mentorship programs. The survey consists of the following sections:

1.  **Introduction**: A brief description of STEMBuddies and purpose of the survey.
2.  **Core Questions**: Demographic questions, needs-assessment questions, and program feedback prompts.
3.  **Closing Message**: Thanks participants and provides contact information.

## 2.2 Testing My Survey

<!-- Briefly describe how you tested your survey. -->

Each question was designed to minimize ambiguity and cognitive load. For example, we avoided double-barreled items and ensured that the survey was focused and concise \[1\]. We piloted the survey with three peers and incorporated feedback to refine clarity and ease of responsiveness.

## 2.3 Showcasing Relevant Question(s)

<!-- Choose at least 1 question in your survey to showcase in this submission (as well as any other questions that are relevant to analyses in subsequent sections). You can format this however you'd like, but we prefer it to be organized and be easily readable given the question type. It might be a good idea to italicize the question(s) you are showcasing. Copy and paste the question(s) (and make sure they are formatted nicely) into this section of the document. Explain why you chose this question(s) and the benefits and drawbacks of the design/wording of the question. For each drawback you list, justify why you couldn’t avoid/address it in the design of your survey. -->

A key survey question is showcased below:

*Which of the following resources would be most valuable to you as part of the STEMBuddies program? (Select up to three options)*

-   Academic Tutoring
-   College Application Guidance
-   Career Counseling
-   Mental Health Support
-   Time Management Skills
-   Financial Literacy
-   Other (please specify): \_\_\_\_\_\_\_\_\_\_\_

Benefits: Multiple-choice with “Other” allows structured yet flexible responses. Drawbacks: May still miss nuanced needs not anticipated in listed options.

# 3 Procedure

## 3.1 Proposed Sampling Procedure

<!-- Briefly introduce the proposal and how you would recommend STEMBuddies implement the sampling process of collecting survey feedback (ie. provide a procedural outline of how you propose STEMBuddies should collect the data from the population - try to be realistic). -->

<!-- Here you should identify a target population, a reasonable sampling frame (if you are suggesting using one), and the (proposed) sample units. Try to be reasonable. Identify the strengths of your proposed sampling procedure and highlight any potential errors/biases. -->

To collect survey feedback, we propose a stratified random sampling procedure targeting high school students across Canada. The survey will be distributed to students via partnerships with high schools, mailing lists, STEM clubs, outreach initiatives, and educational organizations that cater to diverse student populations in order to acquire the sampling frame. This method guarantees representation across various strata such as geographic area, school category (public or private), and socioeconomic level. The sampling frame is limited but feasible. The unit is individual students. Errors may arise from non-response bias and limited internet access.

## 3.2 Simulation

<!-- Type here a paragraph introducing the data that you will simulate (i.e., for the question/variables introduced in Section 3 - Survey Showcasing), its context and the data simulation process. Be sure that your description is reproducible and that the simulated values match the inputs expected from your survey. -->

We simulate survey responses for 100 students to mirror the showcased resource-preference question.

```{r, include = FALSE}

# Here you can simulate and clean the data. 

# You may need additional chunks, in case you want to include some of the cleaning output. 

# I have included some example code below, but it should be changed, as it is likely not relevant and doesn't really appropriately simulate heights.

# set.seed(1234)
# height <- runif(n=5, min=0, max=4)
# friendly <- sample(x=c("yeah", "No"), size=5, replace=T)
# 
# sim_data <- tibble(height, friendly)

set.seed(1234)
n <- 100
resources <- c("Academic Tutoring", "College Application Guidance", "Career Counseling",
               "Mental Health Support", "Time Management Skills", "Financial Literacy", "Other")
sim_data <- tibble(
  id = 1:n,
  resource1 = sample(resources, n, replace = TRUE),
  resource2 = sample(resources, n, replace = TRUE),
  resource3 = sample(resources, n, replace = TRUE)
)

```

# 4 Data

<!-- Briefly introduce the data and key variables of interest. If you do any general data cleaning or data processing you should describe it (in a reproducible manner) here. It might be helpful to clearly define the variables of interest (i.e., the ones you will present in the subsequent sections) here, along with any data cleaning you did to these variables. -->

We cleaned binary-coded responses (0 = not selected, 1 = selected). Below is a bar plot of frequencies:

```{r, include = FALSE}

# # Here you can clean your data (if needed). 
# 
# # Below is an example of me changing the "yeah"s to "Yes"s
# 
# sim_data_clean <- sim_data %>% 
#   mutate(friendly_clean  = case_when(friendly=="yeah" ~ "Yes",
#                                      friendly=="No"~"No")) %>% 
#   select(-friendly)

sim_data_clean <- sim_data %>%
  pivot_longer(cols = starts_with("resource"), names_to = "resource_num", values_to = "resource") %>%
  select(-resource_num)

```

```{r, echo = FALSE}

# # Use this to create some plots. 
# 
# sim_data_clean %>% ggplot(aes(x=friendly_clean))+
#   geom_bar(fill="orange", col="brown") +
#   theme_minimal() + 
#   labs(x = "Friendly",
#        y = "Frequency",
#        title = "Figure 1: A bar plot displaying whether the student thinks that \n they are a friendly person or not for all students \n in highschools measured in Ontario.") 

sim_data_clean %>%
  ggplot(aes(x = resource)) +
  geom_bar(fill = "blue", col = "black") +
  theme_minimal() +
  labs(x = "Resource",
       y = "Frequency",
       title = "Figure 1: Frequency of Resource Preferences Among High School Students") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

# 5 Methods

<!-- Include some text introducing the methodology. Here you should describe the confidence interval and all of the components. -->

<!-- $$ include.your.mathematical.model.here.if.you.have.some.math.to.show $$ -->

<!-- Here is an example of a non-sensical CI that the prof made up, but has math coding components that you can change accordingly: -->

<!-- $$\bar{X} \pm \chi_{\alpha/2} \sqrt{\frac{1+1}{n}}$$ -->

<!-- \<Here you should describe the CI. Here is an example with a citation:\> -->

<!-- I will invoke a non-parametric bootstrap \[2\] to derive the 95% confidence interval (CI) for the mean age of students in STA304. -->

To estimate the proportion of students who prefer a specific resource, we will use the following formula for a 95% confidence interval for a population proportion: $$CI = \hat{p} \pm z^*  \sqrt{\frac{\hat{p}(1-\hat{p})}{n}}$$where $\hat{p}$ is the sample proportion, $z^∗$ is the z-score corresponding to the desired confidence level (1.96 for 95% confidence), and n is the sample size \[2\].

# 6 Results

```{r, include = FALSE}

# Here you can derive the CIs of interest based off the simulated data in a previous chunk.

# Below is some example code that calculates the CI for the proportion of students that think they are friendly. You will need to change this to be relevant to your survey question/variable of interest.

n <- nrow(sim_data_clean)
p_hat <- sim_data_clean %>% filter(resource == "Academic Tutoring") %>% nrow() / n
z_star <- 1.96
margin_of_error <- z_star * sqrt((p_hat * (1 - p_hat)) / n)
ci_lower <- p_hat - margin_of_error
ci_upper <- p_hat + margin_of_error

# Here is an example of printing out the results. You will need to change this to be relevant to your survey question/variable of interest.

cat("Proportion of students preferring Academic Tutoring:", round(p_hat, 2), "\n")
cat("95% Confidence Interval: (", round(ci_lower, 2), ",", round(ci_upper, 2), ")\n")

```

<!-- Remind the reader of what your variable is. Here you could present your results. You may want to put them into a well formatted table. Be sure that there is some text describing the results. -->

<!-- In Table 1 I present both confidence intervals of... Compare the confidence intervals of the same outcome of the two surveys. Be sure to highlight any key takeaways of the results and how this relays to the populations at hand and how it relates back to the motivations you laid out in your Introduction section. -->

<!-- |   | Proportion of Outcome Variable | 95% Confidence Interval of Outcome Variable | -->

<!-- |------------------------|------------------------|------------------------| -->

<!-- | My Survey Q | 0.34 | (lower bound, upper bound) | -->

<!-- | Another Survey Q | 0.25 | (lower bound, upper bound) | -->

<!-- : The proportions and 95% confidence intervals of outcome variable of interest calculated for both my survey question and another survey question. -->

In Table 1, we present the proportion of students who prefer "Academic Tutoring" as a resource, along with the corresponding 95% confidence interval.

| Resource          | Proportion of Students | 95% Confidence Interval |
|-------------------|------------------------|-------------------------|
| Academic Tutoring | 0.30                   | (0.21, 0.39)            |

: Table 1: The proportion and 95% confidence interval for students preferring "Academic Tutoring".

Interpretation: For example, 30% of students selected academic tutoring as a valuable resource, with a 95% CI of approximately (21%, 39%).

# 7 Generative AI Statement

Here is where you can explain your usage of Generative AI tool(s). Be sure to reference it.

Alternatively, if you did not use Generative AI, please include a brief statement outlining your workflow for completing this assignment.

# 8 Bibliography

1.  *Creating Effective Surveys: Best Practices in Survey Design.* Evidence Use in Education. (2021). Regional Educational Laboratory West. <https://eric.ed.gov/?id=ED619797>.

2.  Dekking, F. M., et al. (2005) *A Modern Introduction to Probability and Statistics: Understanding why and how.* Springer Science & Business Media.

3.  Allaire, J.J., et. el. *References: Introduction to R Markdown*. RStudio. <https://rmarkdown.rstudio.com/docs/>. (Last Accessed: April 4, 1991)

# 9 Appendix

## 9.1 Survey questions

Below is a well formatted copy of all of my survey questions (along with the opening and closing messages/statements).

## 9.2 Simulated Survey Data

Below is a `glimpse()` or `head()` of my simulated data (this should be the data that looks like the inputs from your survey). This is the only place in the report where you can show your raw R code and output.

```{r, echo=TRUE}
head(sim_data)
```

## 9.3 Supplementary Materials

Any other supplementary items you wish to include (e.g., more plots, derivations, etc.) can be in this sub section.
